\TheTitle

### 2015-08-17 linvis.tex
Editing: Future Work and Conclusions

\section{Future Work}
This project was implemented over the course of 4 months, interleaved with
other course projects and assignments. There are still many areas that could
use improvements before the full potential of our model can be reached and
understood with our tool. Here, we outline various areas that still need more
attention.

\subsection{Files}
We have limited functionality surrounding files, for both search and presented
information.

There is currently no functionality surrounding searching by filename. Use-case
2 may know what file they are editing and try to determine how it may work with
the other commits and merges in the module. It is possible that a third
use-case may arise, where the user wants to determine all commits that effect a
given file. In both cases, a bottom-to-top approach is used. With this
functionality, implementing the top-to-bottom search feature becomes trivial.

There is limited functionality to the presentation of the file information. At
a minimum, the patches for the commits can be displayed. The patches can then
be used for many more additional features. The patches can be used to piece
together parts of the file to generate a full patch at a given merge rather
than displaying each patch individually. The patches can also be used for
determining what kinds of changes were made, if the lines are being added,
removed, or replaced.

\subsection{Testing}
At this time, we have no evidence that our tool is able to improve the
work-flow of maintainers. We believe that the tool is able to improve the
work-flow and performance of maintainers because it is able to better assist
users because it provides cleaner mechanisms of working with the data. It is
able to provide more relevant information, while removing information that is
irrelevant to a given module or set of merges.

We could perform user-testing, or have some example cases where the tool is
used and the users provide feedback on how it improves or hurts their work
flow.

\subsection{Performance}
The modules and list tree view still use the old method of gathering the
information for the respective view type. For single commits or very small
merges, getting everything directly from the database and performing everything
server-side performs better than using the asynchronous requests, as there
isn't the overhead of multiple round trips; however, as the size of the merges
grow, the performance becomes far worse than the asynchronous system and in
some cases will time out. The asynchronous approach adds some overhead,
profiled at roughly 500ms, regardless of the response size. The asynchronous
approach has many benefits, over building the response on the server, including
the ability to add spinners, which is an improvement to user-experience over
looking at a blank page. Further work can be done to improve the results beyond
the response time of 500ms using improved queries and more efficient methods of
building the tree.

\section{Conclusion}
Our tool shows promising results, providing a clearer picture of the relation
between the merges and commits for sections of the kernel in relation to the
DAG-based models. Not only are we able to provide a clearer visualization, we
are able to provide information about the files edited by all of the commits
contained within a merge.

While we are able to gather a better explanation of the changes happening at
each commit and merge, the tree-model requires more information than what is
provided by git, requiring a central server to monitor changes to the project.
This breaks the design goals of decentralized version control systems and makes
the tool specific to the project.

@@

\balance

>>>>

\section{Future Work}
This project was implemented over four months, interleaved with other course
projects and assignments. There are still many areas that could use
improvements before the full potential of our model can be realized.
Here, we outline various areas that still need more attention.

\subsection{Files}
There is currently no functionality surrounding searching by filename. Use-case
2 may know what file they are editing and try to determine how it may work with
the other commits and merges in the module. It is possible that a third
use-case may arise, where the user wants to determine all commits that effect a
given file. In both cases, a bottom-to-top approach is used. With this
functionality, implementing the top-to-bottom search feature becomes trivial.

There is limited functionality to the presentation of the file information. At
a minimum, the patches for the commits can be displayed. From there, the
patches can be used to piece together parts of the file to generate a single
patch at a given merge rather than displaying each patch individually. The
patches can also be used for determining what kinds of changes were made, if
the lines are being added, removed, or replaced.

\subsection{Testing}
At this time, we have no evidence that our tool is able to improve the
work-flow of maintainers. We believe that the tool is able to improve the
work-flow and performance of maintainers because it provides cleaner mechanisms
of visualizing and presenting the commit information. It is able to provide
more relevant information, while removing information that is irrelevant to a
given module or set of merges.

We can either perform user-testing to show how a users workflow changes, or we
could have maintainers evaluate and critique the tool and use their feedback to
determine if the tool meets our goals.

\subsection{Performance}
The modules and list tree view still use the old method of gathering the
information for the respective view type. For single commits or very small
merges, getting everything directly from the database and generating the pages
server-side performs better than using the asynchronous requests, there
isn't the overhead of multiple round trips. As the size of the merges grow,
the performance becomes far worse than the asynchronous system and in some
cases will time out. The asynchronous approach adds some overhead, profiled at
roughly 500ms, regardless of the response size. The asynchronous approach has
many benefits over building the response on the server, including spinners, a
public API, and lower response times for larger merges. Further work can be
done to improve the results beyond the response time of 500ms using improved
queries and more efficient methods of building the tree. \newpage

\section{Conclusion}
Our tool shows promising results, providing a clearer picture of the relation
between the merges and commits when compared to DAG-based models. Not only are
we provide a clearer visualization, we provide information about the files
edited by all of the commits contained within a merge, and we provide the
information about what modules are edited in a merge.

While we are able to generate a better explanation of the changes happening at
each commit and merge, the tree-model requires more information than what is
provided by git, requiring a central server to monitor changes to the project.
This breaks the design goals of decentralized version control systems and makes
the tool specific to the project.

A tree-based model appears to be sufficient for creating a clean visualization
and explanation of the changes in the Linux kernel.

@@
